Modeling Intervention Strategies for United States TB Control

### 2014-02-15 in_progress/presentations/paper/draft.tex
Working on Methods

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and an extended version of the Hill Model
(Extended Hill Model) were implemented in \texttt{R} as a system of differential
equations, which were solved via the $\texttt{lsoda}$ routine. The systems of
differential equations used to capture basic disease dynamics in the Basic Hill
Model are shown in Figure 2. In the Extended Hill Model, more differential
equations were implemented to add additional tracking and economic modeling.
These equations are detailed in the Appendix, Section 7.2.  Historical data from
2000-2008 was used to initialize the model, which was then run up to the
year 2100.

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.75]{figures/BasicHillEquations.pdf}
  \end{center}
  \caption{System of Differential Equations given in the Hill Model.}
  \label{fig:hillEquations}
\end{figure}

The vector variables $S_{0}, F_{0}, L_{0}, I_{0}, J_{0}$ contain the number of
US-born individuals in the S, F, L, I, J compartments respectively, whereas $S_{1},
F_{1}, L_{1}, I_{1}, J_{1}$ contain foreign-born individuals.  $N_{0}$ and
$N_{1}$ are the total populations of US-born and foreign-born individuals.
The constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$ are death rates.  
A complete list and descriptions of all constants used in the model can be found in the Appendix,
Section 7.1.

@@

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and
their best-fit values. A full listing of constants used in the original Hill
Model can be found in <+CITATION HERE+>. \\
\textit{(USB = US born, FB = Foriegn born)}
\begin{align*}
  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                 population)}\\
  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                 population)}\\
  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
                                 disease)}\\
  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
                                 progressors)}\\
  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
                                 infection)}\\
  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
                                 population)}\\
  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
                                 population)}\\
  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
                                 acute infection)}\\
  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
                                 active disease)}\\
  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
                                 population for USB)}\\
  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
                                population for FB)}\\
\end{align*}
\subsection{The Extended Hill Equations}
Below, we detail some of the relevant equations used in the extended hill model.
In many cases, the equations of the Hill model were split into their component
parts, which could then be tracked separately.

>>>>

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and our extended Model (Extended Hill
Model) were implemented in \texttt{R} as a system of differential equations,
which were solved via the $\texttt{lsoda}$ routine. The systems of differential
equations used to capture basic disease dynamics in the Basic Hill Model are
shown in Figure~\ref{fig:hillEquations}. In the Extended Hill Model, more
differential equations were implemented to add additional tracking and economic
modeling. These equations are detailed in the\\
{\huge\color{red} Should appendix be capitalized? What about Figure?}\\
appendix,
section~\ref{sec:extendedHillEqs}.  Historical data from 2000-2008 was used to
initialize the model, which was then run up to the year 2100.

\begin{figure} 
  {\huge\color{red} Make this not a figure. This should definitely just be tex.}
  \begin{center}
    \includegraphics[scale=0.75]{figures/BasicHillEquations.pdf}
  \end{center}
  \caption{System of Differential Equations given in the Hill Model.}
  \label{fig:hillEquations}
\end{figure}

The vector variables $S_0, F_0, L_0, I_0, J_0$ contain the number of US-born
individuals in the S, F, L, I, J compartments respectively, whereas $S_1, F_1,
L_1, I_1, J_1$ contain the number of foreign-born individuals. $N_0$ and $N_1$
are the total populations of US-born and foreign-born individuals.  The
constants $\rho$ and $\alpha$ are birth rates, while $\mu_{i}$, and $\mu_{d}$
are death rates. A complete list and descriptions of all constants used in the
model can be found in the Appendix, Section~\ref{subsec:hillConstants}.

@@

\section{Appendix}
\subsection{Hill Constants}
\label{subsec:hillConstants}
Below, we detail some of the relevant constants in the Basic Hill Model, and
their best-fit values. A full listing of constants used in the original Hill
Model can be found in <+CITATION HERE+>. \\
\textit{(USB = US born, FB = Foriegn born)}
\begin{align*}
  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                 population)}\\
  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                 population)}\\
  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
                                 disease)}\\
  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
                                 progressors)}\\
  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
                                 infection)}\\
  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
                                 population)}\\
  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
                                 population)}\\
  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
                                 acute infection)}\\
  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
                                 active disease)}\\
  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
                                 population for USB)}\\
  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
                                population for FB)}\\
\end{align*}
\subsection{The Extended Hill Equations}
\label{sec:extendedHillEqs}
Below, we detail some of the relevant equations used in the extended hill model.
In many cases, the equations of the Hill model were split into their component
parts, which could then be tracked separately.
